Improving credibility and efficiency of decision-making \\ within democratic communities via a statistical quorum

### 2018-04-19 statistical-quorum.tex
90% is just a question of community, not universal constant. This column does not add anything.
You can add this to caption, if you want. Discussion that they are below
a resonable number like 90%.

\begin{table}
  \centering
  \begin{small}
  \begin{tabular}{l r r r r r r r r}
    {\small\textit{Vote}} & \multicolumn{2}{r}{\small \textit{First option}} & \multicolumn{2}{r}{\small \textit{Second option}} & {\small \textit{Total eligible}} & {\small \textit{Turnout}} & {\small \textit{Decision}} \\
    & & & & & {\small \textit{voters}} & & {\small \textit{credibility}} & {\small \textit{>$90\%$}}\\
    \midrule
    Brexit & 17,410,742 & $51.9\%$ & 16,141,241 & $48.1\%$ & 46,500,001 & $72.2\%$ & $59.8\%$ & \textbf{No}\\
    Presidential elections & 62,984,825 & $48.9\%$ & 65,853,516 & $51.1\%$ & 230,585,915 & $55.9\%$ & $52.6\%$ & \textbf{No}\\
  \end{tabular}
  \end{small}
  \bigskip\caption{Votes cast in Brexit, a 2016 referendum for United Kingdom's withdrawal from the European Union~\protect\cite{brexitresults},
  and 2016 USA presidential elections, popular vote~\protect\cite{usaresults1,usaresults2}. Simplified to only two options and without
  invalid votes. The last column shows computed decision credibility as described in Section~\ref{sec:decision-credibility}. We see that
  credibility is low, which we can mostly attribute to the fact that there is small difference in votes between both options so with a larger turnout, any option could have ended up winning.}\label{tab:example}
  \vspace{-0.3cm}
\end{table}

>>>>

\begin{table}
  \centering
  \begin{small}
  \begin{tabular}{l r r r r r r r}
    {\small\textit{Vote}} & \multicolumn{2}{r}{\small \textit{First option}} & \multicolumn{2}{r}{\small \textit{Second option}} & {\small \textit{Total eligible}} & {\small \textit{Turnout}} & {\small \textit{Decision}} \\
    & & & & & {\small \textit{voters}} & & {\small \textit{credibility}} \\
    \midrule
    Brexit & 17,410,742 & $51.9\%$ & 16,141,241 & $48.1\%$ & 46,500,001 & $72.2\%$ & $59.8\%$ \\
    Presidential elections & 62,984,825 & $48.9\%$ & 65,853,516 & $51.1\%$ & 230,585,915 & $55.9\%$ & $52.6\%$ \\
  \end{tabular}
  \end{small}
  \bigskip\caption{Votes cast in Brexit, a 2016 referendum for United Kingdom's withdrawal from the European Union~\protect\cite{brexitresults},
  and 2016 USA presidential elections, popular vote~\protect\cite{usaresults1,usaresults2}. Simplified to only two options and without
  invalid votes. The last column shows computed decision credibility as described in Section~\ref{sec:decision-credibility}. We see that
  credibility is low, which we can mostly attribute to the fact that there is small difference in votes between both options so with a larger turnout, any option could have ended up winning.}\label{tab:example}
  \vspace{-0.3cm}
\end{table}
